\documentclass[11pt, letterpaper]{article}

% Essential Packages
\usepackage[margin=0.5in]{geometry} % Sets margins
\usepackage{titlesec}               % Custom section formatting
\usepackage{enumitem}               % Custom list formatting
\usepackage{hyperref}               % Clickable links

% Formatting adjustments
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}
\setlength{\parindent}{0pt}

% Link colors
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
}

\begin{document}

% --- HEADER ---
\begin{center}
    {\huge \textbf{Jeremiah Harsojo}} \\ \vspace{2pt}
    Berkeley, CA $|$ \href{mailto:jeremiahn.harsojo@gmail.com}{jeremiahn.harsojo@gmail.com} $|$ (559) 321-5659 \\
    \href{https://github.com/jeremiahharsojo}{github.com/jeremiahharsojo} $|$ \href{https://linkedin.com/in/jeremiahharsojo}{linkedin.com/in/jeremiahharsojo}
\end{center}

% --- EDUCATION ---
\section{Education}
\textbf{University of California, Berkeley} \hfill Berkeley, CA \\
Bachelor of Science in Computer Science \hfill Expected May 2026 \\
\textbf{Relevant Coursework:} Computer Graphics (CS184), Database Systems (CS186), Data Structures, Algorithms

% --- TECHNICAL SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Languages:} C++, Python, Go, Java, SQL, LaTeX, Rust
    \item \textbf{Tools \& Environments:} Git, uv, Linux, VSCode, SQLite
\end{itemize}

% --- PROJECTS ---
\section{Projects}

\textbf{Distance-Vector Routing Protocol} | \textit{Python} \hfill \textit{Spring 2025}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
\item Developed a routing protocol implementing Bellman-Ford updates and route advertisement for dynamic topology discovery.
\item Integrated loop-prevention strategies including Split Horizon, Poison Reverse, and Poisoning Expired Routes.
\item Engineered incremental triggered updates to optimize network convergence and minimize control plane overhead.
\end{itemize}

\textbf{Reliable Transport Protocol (TCP)} | \textit{Python} \hfill \textit{Spring 2025}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
\item Built a reliable transport layer from scratch, implementing the TCP Three-Way Handshake and connection teardown.
\item Developed sliding window flow control and sequence number management using 32-bit modular arithmetic.
\item Implemented RTT estimation and retransmission timeouts (RTO) to ensure reliability over lossy network channels.
\end{itemize}

\textbf{Relational Database Implementation} $|$ \textit{Java} \hfill \textit{Spring 2026}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Implemented a B+ Tree index, managing LeafNode and InnerNode splitting operations.
    \item Engineered core database methods including \texttt{get}, \texttt{put}, and \texttt{bulkLoad} to optimize search and insertion performance.
\end{itemize}

\textbf{Software Rasterizer} $|$ \textit{C++} \hfill \textit{Spring 2026}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Built a software rasterizer to draw triangles, implementing supersampling for antialiasing.
    \item Developed texture mapping capabilities utilizing barycentric coordinates.
    \item Implemented halfedge data structures to support mesh operations like edge flipping and splitting.
\end{itemize}


% --- EXPERIENCE ---
\section{Work Experience}
\textbf{The Student Senate for California Community Colleges} \hfill Bay Area, CA \\
\textit{Student Intern} \hfill \textit{August 2023 -- July 2024}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Coordinated communication between colleges in the Bay Area, mastering professional workplace etiquette and organizational dynamics
    \item Conducted educational meetings on legal decisions as well as parliamentary procedure
\end{itemize}

\end{document}